Abstract

### 2025-05-27 output/Letter_to_editor_reviewers.Rmd
Correct errata and style
In response to "dimensional sensitivity" comment

To our understanding, one may assume a theoretical dimensional sensitivity of a test space that is higher than the dimensionality of the latent space.
We acknowledge we may have overlooked this distinction.
However, in such a case, the (minimum) dimensionality of the data would be "the smaller of the dimensions or variation for the people and the dimensions of sensitivity for the test items" (@reckase_multidimensional_2009, p. 182).
That is, the dimensional sensitivity of the data would nevertheless be restricted by the dimensionality of the latent space.
This implies that the parameter values one can estimate for the items will represent a lower-dimensional solution, which would be the projection of the theoretically higher-dimensionally sensitive parameters on the lower-dimensional latent trait space, as discussed in p. 182 of @reckase_multidimensional_2009.
In practice, this implies that this solution is indistinguishable from one where the items are simply sensitive to the lower number of dimensions, with their parameters given by such lower-dimensional solution which would correspond to their projections from the alleged higher-dimensional space onto the lower-dimensional one.

@@

> [...] In that example,
he uses a covariance matrix that practically has rank 1,
implying that the (alleged) three latent dimensions collapse into a single one.
This makes the latent space unidimensional in practice,
which in turn resticts the dimensionality of any response dataset
generated from a test measuring those traits.
Therefore, "the data could be well fit by a unidimensional IRT model"
[@reckase_multidimensional_2009, p. 189].
In such a case, when all the items are strictly aligned with
the one dimension being measured,
we should expect the direction angles to be extremely close to 0 for all items.
The reader interested can check that this is the case for
the covariance-based version of the direction angles
in the table in Online Resource 1.

>>>>

To our understanding, one may assume a theoretical dimensional sensitivity of a test space that is higher than the dimensionality of the latent space, which we acknowledge we may have overlooked.
However, in such a case, the (minimum) dimensionality of the data would be "the smaller of the dimensions or variation for the people and the dimensions of sensitivity for the test items" (@reckase_multidimensional_2009, p. 182).
That is, the dimensional sensitivity of the data would nevertheless be restricted by the dimensionality of the latent space.
This implies that the parameter values one can estimate for the items will represent a lower-dimensional solution, which would be the projection of the theoretically higher-dimensionally sensitive parameters on the lower-dimensional latent trait space, as discussed in p. 182 of @reckase_multidimensional_2009.
In practice, this implies that this solution is indistinguishable from one where the items are simply sensitive to the lower number of dimensions, with their parameters given by such lower-dimensional solution which would correspond to their projections from the alleged higher-dimensional space onto the lower-dimensional one.

@@

> [...] In that example,
he uses a covariance matrix that practically has rank 1,
implying that the (alleged) three latent dimensions collapse into a single one.
This makes the latent space unidimensional in practice,
which in turn restricts the dimensionality of any response dataset
generated from a test measuring those traits.
Therefore, "the data could be well fit by a unidimensional IRT model"
[@reckase_multidimensional_2009, p. 189].
In such a case, when all the items are strictly aligned with
the one dimension being measured,
we should expect the direction angles to be extremely close to 0 for all items.
The reader interested can check that this is the case for
the covariance-based version of the direction angles
in the table in Online Resource 1.

### 2025-05-27 output/Main_text.Rmd
Correct errata and style
In response to "dimensional sensitivity" comment

The latter effect can be better noticed in another case, in which Reckase
uses the same item parameters to demonstrate the over-specification of
dimensions (see p. 183).
In that example, he uses a covariance matrix that practically has rank 1,
implying that the (alleged) three latent dimensions collapse into a single one.
This makes the latent space unidimensional in practice,
which in turn resticts the dimensionality of any response dataset
generated from a test measuring those traits.
Therefore, "the data could be well fit by a unidimensional IRT model"
[@reckase_multidimensional_2009, p. 189].
In such a case, when all the items are strictly aligned with
the one dimension being measured,
we should expect the direction angles to be extremely close to 0 for all items.
The reader interested can check that this is the case for
the covariance-based version of the direction angles
in the table in Online Resource 1.

>>>>

The latter effect can be better noticed in another case, in which Reckase
uses the same item parameters to demonstrate the over-specification of
dimensions (see p. 183).
In that example, he uses a covariance matrix that practically has rank 1,
implying that the (alleged) three latent dimensions collapse into a single one.
This makes the latent space unidimensional in practice,
which in turn restricts the dimensionality of any response dataset
generated from a test measuring those traits.
Therefore, "the data could be well fit by a unidimensional IRT model"
[@reckase_multidimensional_2009, p. 189].
In such a case, when all the items are strictly aligned with
the one dimension being measured,
we should expect the direction angles to be extremely close to 0 for all items.
The reader interested can check that this is the case for
the covariance-based version of the direction angles
in the table in Online Resource 1.
